Gap formation and stability in non-isothermal protoplanetary discs

### 2015-02-25 paper/results.tex
Near final update

Fig.\ref{planetofflifetimeplot} shows evolution of the $m=1$ surface
density component, which represents the amplitude of the post-merger
single vortex. For completeness we also ran intermediate cases with
$\tilde{\beta}=0.5$ and $5.0$. The amplitude of the initially formed vortex was 
found to decrease with increased cooling rate. The vortices simply decay on a
timescale of $O(10^3)$ orbits with faster decay for stronger vortices
(which are obtained with faster cooling rates). {\bf This decay is 
  probably due to numerical viscosity. During the slow decay the
  vortex elongates (weakens) while its radial width remains $O(H)$, so
  its surface density decreases. (true?)} 
We will see in the
next section that this behaviour {\bf after linear growth} is very
different to when the planet potential is kept on.

@@

{\bf For comparison we also ran a locally isothermal simulation to
  compare with the case with rapid cooling ($\tilde{\beta}=0.01$), but
  did not observe significant vortex decay within our simulation
  timescale in the former case. This suggests there could be
  fundamental differences between the two cases.}

@@

{\bf During the quasi-steady state the vortex 
  orbits at $r\sim r_p+6r_h$. We do not see significant
  vortex migration at this stage (true?), since the vortex is located at a
  surface density maximum, which can trap vortices
  \citep{paardekooper10}. However, simultaneous with the
  appearence of the wakes, we observe the vortex begins to migrate 
  inwards to $r\sim r_p+5r_h$. 
  % This is a result of the the spiral waves transporting
  % angular momentum to the disk (Is this true? Shocks on the inner disk
  % seem stronger so I would think it would migrate outward). 
  }

@@

This can be interpreted as the vortex providing a viscosity;  
and we measure a typical alpha viscosity $\alpha = O(10^{-2})$
associated with the vortex. This acts against gap-opening
by the planet {\bf, and smooths out the outer surface density bump,    
} so the condition for the RWI 
becomes less favourable. {\bf In
  order to re-launch the RWI, the surface density bump should
  reform. However, this is difficult as there is no more material
  in the planet's vicinity to clear out (Fig. \ref{gap_smoothed}).} {\bf This may} may explain
why vortices do  not reform again (at least within the simulation timescale). 
{\bf what is aspect-ratio at outer gap edge after full decay?}

>>>>

Fig.\ref{planetofflifetimeplot} shows evolution of the $m=1$ surface
density component, which represents the amplitude of the post-merger
single vortex. For completeness we also ran intermediate cases with
$\tilde{\beta}=0.5$ and $5.0$. The amplitude of the initially formed vortex was 
found to decrease with increased cooling rate. The vortices simply decay on a
timescale of $O(10^3)$ orbits with faster decay for stronger vortices
(which are obtained with faster cooling rates). {\bf This decay is 
  probably due to numerical viscosity. During the slow decay the
  vortex elongates (weakens) while its radial width remains $O(H)$, so
  its surface density decreases. (true?) (For isothermal and long cases yes. Spiral waves appear in beta=0.1,0.5,1.0})
We will see in the
next section that this behaviour {\bf after linear growth} is very
different to when the planet potential is kept on.

@@

{\bf For comparison we also ran a locally isothermal simulation with results concident with those found in this section.
}

%{\bf For comparison we also ran a locally isothermal simulation to
%  compare with the case with rapid cooling ($\tilde{\beta}=0.01$), but
%  did not observe significant vortex decay within our simulation
%  timescale in the former case. This suggests there could be
%  fundamental differences between the two cases.}

@@

{\bf During the quasi-steady state the vortex 
  orbits at $r\sim r_p+6r_h$. We do not see significant
  vortex migration at this stage (true?:yes), since the vortex is located at a
  surface density maximum, which can trap vortices
  \citep{paardekooper10}. However, simultaneous with the
  appearence of the wakes, we observe the vortex begins to migrate 
  inwards to $r\sim r_p+5r_h$. 
  % This is a result of the the spiral waves transporting
  % angular momentum to the disk (Is this true? Shocks on the inner disk
  % seem stronger so I would think it would migrate outward). 
  }

@@

This can be interpreted as the vortex providing a viscosity;  
and we measure a typical alpha viscosity $\alpha = O(10^{-2})$
associated with the vortex. This acts against gap-opening
by the planet {\bf, and smooths out the outer surface density bump,    
} so the condition for the RWI 
becomes less favourable. {\bf In
  order to re-launch the RWI, the surface density bump should
  reform. However, this is difficult as there is no more material
  in the planet's vicinity to clear out (Fig. \ref{gap_smoothed}).} {\bf This may} may explain
why vortices do  not reform again (at least within the simulation timescale). 
{\bf After full decay the aspect ratio at the outer gap edge is $h\sim0.05$}
% (0.06 for beta=5.0,10)}

% what is aspect-ratio at outer gap edge after full decay?
